Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-03-19 Documents/Euler/Benchmarks1D/draft.tex
Merged figures
combined figures and shrank margins

@@

Several tests were used to assess the accuracy of the integration method \citep{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & $T$ \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{Initial parameters for most of the tests described in this paper, from \citep{LiskaWendroff2003}~and \citep{Leveque2002}. The table shows initial density ($\rho$), velocity ($u$), and pressure ($p$) on both sides of a discontinuity located at $x_0$. These initial conditions are then advanced to time $T$.}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. 
The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, $x_{\mbox{\tiny L}}=0.1$ and $x_{\mbox{\tiny R}}=0.6$ in test 9 \citep{LiskaWendroff2003}, $x_{\mbox{\tiny L}}=-5$ and $x_{\mbox{\tiny R}}=15$ in test 10, and $x_{\mbox{\tiny L}}=-15$ and $x_{\mbox{\tiny R}}=5$ in test 11 \citep{Leveque2002}. 
\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}

@@

First, the tests were run with values computed at different intervals; the method of integration is the same in each test. Between the two endpoints, 128, 256, 512, and 1024 points were computed for on each respective test. Figures~\ref{fig:dencellcomp_20}--\ref{fig:pvcellcomp} show results of these tests:
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=.95\textwidth]{dencellcomp_20}
  \end{center}
  \caption{Results showing the density for Sod's shock tube at $t=0.2$, computed with the first-order method using different number of elements: 128 (solid red), 256 (dashed green), 512 (dotted blue), and 1024 (dash-dot pink).  The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted cyan line.}
  \label{fig:dencellcomp_20}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{velcellcomp_20} &
      \includegraphics[width=.475\textwidth]{prscellcomp_20}
    \end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:dencellcomp_20}:
  velocity (left panel) and pressure (right panel).}
  \label{fig:pvcellcomp}
\end{figure}
%\newpage

%\clearpage
%\begin{figure}
 % \begin{center}

 % \end{center}
 % \caption{velocity}
 % \label{fig:velcellcomp_20}
%\end{figure}
%\clearpage
Next, several tests were run of different integration methods; the number of points was held constant at 128 each time. Higher numbers in the key correspond to higher-order, more exact methods of integration.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.95\textwidth]{den128comp_20}
  \end{center}
  \caption{Results showing the density for Sod's shock tube at $t=0.2$, computed with 128 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den128comp}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel128comp_20} &
	  \includegraphics[width=.475\textwidth]{prs128comp_20}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den128comp}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

This test is the same as Sod's shock tube from the previous section, except that there is a non-zero velocity to the left of the initial discontinuity.  
As a result, a sonic point develops in the rarefaction wave.  
For subsequent tests, the number of cells was consistent within each test, and the integration method was varied as in the first test. 
The graphs for the second test show a result common throughout many of the different tests: The first order integration method is considerably far from the exact solution; the second and third order integration methods yield nearly identical results which are near, but not exactly equal to, the exact solution. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T2.png}	
  \end{center}
  \caption{Results showing the density for test 2 at $t=0.2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T2}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T2.png} &
	  \includegraphics[width=.475\textwidth]{prs_T2.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T2}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

This test shows results similar to Toro's Riemann Problem. The deviation of experimental results from exact is especially noticeable in velocity. Near the initial point of discontinuity, the exact results appear completely horizontal. Method 1 almost completely ignores this horizontal part, while Methods 2 and 3 smooth it out considerably. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T3.png}	
  \end{center}
  \caption{Results showing the density for the double rarefaction problem at $t=0.15$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T3}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T3.png} &
	  \includegraphics[width=.475\textwidth]{prs_T3.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T3}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T4.png}	
  \end{center}
  \caption{Results showing the density for the Noh problem at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T4}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T4.png} &
	  \includegraphics[width=.475\textwidth]{prs_T4.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T4}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T5.png}	
  \end{center}
  \caption{Results showing the density for test 5 at $t=0.012$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T5}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T5.png} &
	  \includegraphics[width=.475\textwidth]{prs_T5.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T5}:
  velocity (left panel) and pressure (right panel).}
\end{figure}
\clearpage

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T6.png}	
  \end{center}
  \caption{Results showing the density for test 6 at $t=0.035$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T6}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T6.png} &
	  \includegraphics[width=.475\textwidth]{prs_T6.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T6}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T7.png}	
  \end{center}
  \caption{Results showing the density for the stationary contact discontinuity test at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T7}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T7.png} &
	  \includegraphics[width=.475\textwidth]{prs_T7.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T7}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\subsection{Test 8: Moving Contact Discontinuity}
This test features a contact discontinuity at $x=0.7$. In density, this test shows a small blip around $x=0.7$ that is unique to the second order method. Velocity and pressure are both constant throughout. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T8.png}	
  \end{center}
  \caption{Results showing the density the moving contact discontinuity test at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T8}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T8.png} &
	  \includegraphics[width=.475\textwidth]{prs_T8.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T12_2000.png}	
  \end{center}
  \caption{Results showing the density for the Woodward-Collela blast wave problem at $t=0.038$, computed with 2000 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).}
  \label{fig:den_T12_2000}
\end{figure}

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{vel_T12_2000.png}
     \includegraphics[width=.475\textwidth]{prs_T12_2000.png}	
    \end{tabular}
  \end{center}
 \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T12_2000}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T12_400.png}	
  \end{center}
  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_2000}~computed with 400 cells. The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
  \label{fig:den_T12_400}
\end{figure}

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{vel_T12_400.png}
     \includegraphics[width=.475\textwidth]{prs_T12_400.png}	
    \end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T12_400}:
  velocity (left panel) and pressure (right panel)}
\end{figure}

>>>>

\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{1.75in}

\addtolength{\topmargin}{-.875in}
\addtolength{\textheight}{1.75in}

@@

Several tests were used to assess the accuracy of the integration method \citep{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & $T$ \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & -1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{Initial parameters for most of the tests described in this paper, from \citep{LiskaWendroff2003}~and \citep{Leveque2002}. The table shows initial density ($\rho$), velocity ($u$), and pressure ($p$) on both sides of a discontinuity located at $x_0$. These initial conditions are then advanced to time $T$.}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. 
The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, $x_{\mbox{\tiny L}}=0.1$ and $x_{\mbox{\tiny R}}=0.6$ in test 9 \citep{LiskaWendroff2003}, $x_{\mbox{\tiny L}}=-5$ and $x_{\mbox{\tiny R}}=15$ in test 10, and $x_{\mbox{\tiny L}}=-15$ and $x_{\mbox{\tiny R}}=5$ in test 11 \citep{Leveque2002}. 
\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}

@@

First, the tests were run with values computed at different intervals; the method of integration is the same in each test. Between the two endpoints, 128, 256, 512, and 1024 points were computed for on each respective test. Figure~\ref{fig:dencellcomp_20} shows results of these tests:
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=.95\textwidth]{dencellcomp_20}
    \begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{velcellcomp_20} &
      \includegraphics[width=.475\textwidth]{prscellcomp_20}
    \end{tabular}
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for Sod's shock tube at $t=0.2$, computed with the first-order method using different number of elements: 128 (solid red), 256 (dashed green), 512 (dotted blue), and 1024 (dash-dot pink).  The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted cyan line.}
  \label{fig:dencellcomp_20}
\end{figure}

Next, several tests were run of different integration methods; the number of points was held constant at 128 each time. Higher numbers in the key correspond to higher-order, more exact methods of integration.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.975\textwidth]{den128comp_20}
    \begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel128comp_20} &
      \includegraphics[width=.475\textwidth]{prs128comp_20}
    \end{tabular}
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for Sod's shock tube at $t=0.2$, computed with 128 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den128comp}
\end{figure}

@@

This test is the same as Sod's shock tube from the previous section, except that there is a non-zero velocity to the left of the initial discontinuity.  
As a result, a sonic point develops in the rarefaction wave.  
For subsequent tests, the number of cells was consistent within each test, and the integration method was varied as in the first test. 
The graphs for the second test show a result common throughout many of the different tests: The first order integration method is considerably far from the exact solution; the second and third order integration methods yield nearly identical results which are near, but not exactly equal to, the exact solution. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T2.png}
	 \begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T2.png} &
	  \includegraphics[width=.475\textwidth]{prs_T2.png}
	 \end{tabular}	
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for test 2 at $t=0.2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T2}
\end{figure}

@@

This test shows results similar to Toro's Riemann Problem. The deviation of experimental results from exact is especially noticeable in velocity. Near the initial point of discontinuity, the exact results appear completely horizontal. Method 1 almost completely ignores this horizontal part, while Methods 2 and 3 smooth it out considerably. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T3.png}	
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T3.png} &
	  \includegraphics[width=.475\textwidth]{prs_T3.png}
	\end{tabular}
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the double rarefaction problem at $t=0.15$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T3}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T4.png}	
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T4.png} &
	  \includegraphics[width=.475\textwidth]{prs_T4.png}
	\end{tabular}
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the Noh problem at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T4}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T5.png}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T5.png} &
	  \includegraphics[width=.475\textwidth]{prs_T5.png}
	\end{tabular}	
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for test 5 at $t=0.012$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T5}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T6.png}	
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T6.png} &
	  \includegraphics[width=.475\textwidth]{prs_T6.png}
	\end{tabular}
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for test 6 at $t=0.035$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T6}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T7.png}	
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T7.png} &
	  \includegraphics[width=.475\textwidth]{prs_T7.png}
	\end{tabular}
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the stationary contact discontinuity test at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T7}
\end{figure}

@@

\subsection{Test 8: Moving Contact Discontinuity}
This test features a contact discontinuity at $x=0.7$. In density, this test shows a small blip around $x=0.7$ that is unique to the second order method. Velocity and pressure are both constant throughout. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T8.png}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T8.png} &
	  \includegraphics[width=.475\textwidth]{prs_T8.png}
	\end{tabular}
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the moving contact discontinuity test at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T8}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T12_2000.png}
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{vel_T12_2000.png}
     \includegraphics[width=.475\textwidth]{prs_T12_2000.png}	
    \end{tabular}	
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the Woodward-Collela blast wave problem at $t=0.038$, computed with 2000 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).}
  \label{fig:den_T12_2000}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T12_400.png}	
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{vel_T12_400.png}
     \includegraphics[width=.475\textwidth]{prs_T12_400.png}	
    \end{tabular}
  \end{center}
  \caption{Results for the density (top), velocity (bottom left), and pressure (bottom right) from the same experiments as shown in Figure~\ref{fig:den_T12_2000}~computed with 400 cells. The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
  \label{fig:den_T12_400}
\end{figure}
